---
output:
  github_document:
    toc: FALSE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# kfa: K-Fold Cross-Validation For Factor Analysis

[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/kfa)](https://cran.r-project.org/package=kfa)
[![metacran downloads](https://cranlogs.r-pkg.org/badges/kfa)](https://cran.r-project.org/package=kfa) 
[![metacran downloads](https://cranlogs.r-pkg.org/badges/grand-total/kfa)](https://cran.r-project.org/package=kfa)

**kfa** provides utilities for examining the dimensionality of a set of variables to foster scale development. Harnessing a k-fold cross-validation approach, **kfa** helps researchers compare possible factor structures and identify which structures are plausible and replicable across samples.

## Installation

```{r, eval = FALSE}
# From CRAN
install.packages("kfa")

# Development version
install.packages("remotes")
remotes::install_github("knickodem/kfa")

library(kfa)
```

## Workflow

The two primary functions are `kfa()` and `kfa_report()`. When the set of potential variables and (optionally) the maximum number of factors, *m*, are supplied to `kfa()`, the function:

* (if requested) conducts a power analysis to determine the number of folds, *k*, on which to split the data into training and testing samples
* creates *k* folds (i.e. the training and testing samples).

Then for each fold:

* calculates sample statistics (e.g., correlation matrix, thresholds [if necessary]) from training sample.
* runs 2:*m* factor exploratory factor analysis (EFA) models using the sample statistics, applies rotation (if specified), and
extracts the factor structure for a confirmatory factor analysis (CFA). The structure for a 1-factor CFA is also defined.
* runs the 1:*m* factor CFA models on the testing sample.

The factor analyses are run using the `lavaan` package with many of the `lavaan` estimation and missing data options available for use in `kfa()`. `kfa()` returns a list of lists with *k* outer elements for each fold and *m* inner elements for each replicable factor model, each containing a `lavaan` object. To expedite running *k* x *m* x 2 (EFA and CFA) models, the function utilizes the `parallel` and `foreach` packages for parallel processing.

```{r, eval = FALSE}
library(kfa)
# simulate data based on a 3-factor model with standardized loadings
sim.mod <- "f1 =~ .7*x1 + .8*x2 + .3*x3 + .7*x4 + .6*x5 + .8*x6 + .4*x7
                f2 =~ .8*x8 + .7*x9 + .6*x10 + .5*x11 + .5*x12 + .7*x13 + .6*x14
                f3 =~ .6*x15 + .5*x16 + .9*x17 + .4*x18 + .7*x19 + .5*x20
                f1 ~~ .2*f2
                f2 ~~ .2*f3
                f1 ~~ .2*f3
                x9 ~~ .2*x10"
set.seed(1161)
sim.data <- simstandard::sim_standardized(sim.mod,
                                          n = 900,
                                          latent = FALSE,
                                          errors = FALSE)[c(2:9,1,10:20)]

# include a custom 2-factor model
custom2f <- paste0("f1 =~ ", paste(colnames(sim.data)[1:10], collapse = " + "),
                   "\nf2 =~ ",paste(colnames(sim.data)[11:20], collapse = " + "))

mods <- kfa(variables = sim.data,
            k = NULL, # prompts power analysis to determine number of folds
            custom.cfas = custom2f)

```


`kfa_report()` then aggregates the CFA model fit, parameter estimates, and model-based reliability across folds for each factor structure extracted in `kfa()`. The results are then organized and exported via `rmarkdown`, such as the [example report](https://htmlpreview.github.io/?https://github.com/knickodem/kfa/blob/main/README%20Example%20Reports/example_sim_kfa_report.html) run below.

```{r, eval = FALSE}
# Run report
kfa_report(mods, file.name = "example_sim_kfa_report",
           report.title = "K-fold Factor Analysis - Example Sim"
           report.format = "html_document")
```


## Under Development and Consideration

* **Clustered Data** - The package does not currently account for clustered data. Future versions will utilize the cluster argument from `lavaan` to estimate cluster robust standard errors when calculating the correlation matrix for the factor analyses. We are also considering how to account for nesting structures in the creation of the folds, which are currently created assuming a simple random sample. If so, we will also incorporate cluster adjustments for the power analysis determining the value of *k*.


