
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
flextable::set_flextable_defaults(fonts_ignore = TRUE)
# knitr::opts_chunk$set(options(knitr.kable.NA = ''))

plot.settings <- list(what = "std", whatLabels = "no", layout = "tree",
                        intercepts = FALSE, residuals = FALSE, thresholds = FALSE,
                        cut = load.flag, posCol = c("#BF0000","#000000"), fade = FALSE,
                        # edge.color = , # could create custom function to utilize this argument
                        weighted = TRUE, negDashed = TRUE, esize = 5,
                        manifests = vnames, reorder = FALSE)
border <- officer::fp_border(width = 2) # manual horizontal flextable border width

```

---
title: "`r report.title`"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
---

# Fold and Sample Summary

**# of folds:** `r k`

**# of variables:** `r nvars`

**# of observations:** `r nobs`

**Maximum # of factors:**

 - Allowed - `r fac.allow`
 - Extracted - `r fac.max`

\newpage

# Model Summary

**Fit across folds by factor model**

```{r model fit, ft.align = "left", results='asis'}
index <- index[index != "df"] 
fit.map <- data.frame(col_keys = names(fit.table),
                      top = c("model", "df", rep(index, each = 2)),
                      bottom = c("model", "df", rep(c("mean", "range"), times = length(index))))

fit.flex <- flextable::flextable(fit.table)
fit.flex <- flextable::colformat_double(fit.flex, j = -c(1,2), digits = digits)
fit.flex <- two_level_flex(fit.flex, mapping = fit.map, vert.cols = c("model", "df"), border = border)
knit_print(fit.flex)
```


**Count of folds out of `r k` with flagged problems**

```{r flagged, ft.align = "left", results='asis'}
flagged.flex <- flextab_format(flagged, bold.type = "none", width = width, digits = digits)
knit_print(flagged.flex)
```

*Notes:*  
"common structure" is the number of folds the EFA identified the most common structure. Thus, "common structure" will be `r k` when the same structure was identified in every fold and < `r k` when multiple factor structures were identified. The most common structure was used in the CFA. See Appendix for all structures.
"improper solution" is the number of folds with non-convergence or a non-positive definite matrix.
"high factor correlation" threshold set to `r cor.flag`.  
"low scale reliability" threshold set to `r rel.flag` with $\omega_h$.  
"low loading" threshold set to `r load.flag`.  
blanks = not applicable  


```{r best model, ft.align = "left", results='asis', eval=FALSE}
cat("**Best model in each fold by fit index**")
best.flex <- flextab_format(best.model, bold.type = "none", digits = digits)
knit_print(best.flex)
```


# Model Details

```{r structure, ft.align = "left", results = 'asis', warning = FALSE, message = FALSE, fig.height = 4, fig.width = 6}

for(n in 1:m){
  cat("##", model.names[[n]])
  cat("\n\n")
  cat("**Factor Structure**")
  cat("\n\n")
  cat(gsub("\n", "\n\n", kstructures[[n]][[1]]$structure))
  cat("\n\n")
  # l <- length(kstructures[[n]][[1]]$folds)
  # plotmat <- matrix(1:l, nrow = ifelse(l < 4, 1, 2), byrow = TRUE)
  # graphics::layout(plotmat)
    do.call(semPlot::semPaths, args = c(list(object = kfa$cfas[[1]][[n]],
                                           color = list(lat = palette.colors(n = n + 1, palette = "Okabe-Ito",
                                                        recycle = TRUE)[-1]),
                                           title = FALSE),
                                      plot.settings))
    # title(paste("Fold:", f), adj = 0, line = 0)
  cat("\n\n")
  cat("**Standardized Loading Across Folds**")
  cat("\n\n")
  lambda.flex <- flextab_format(klambdas$loadings[[n]], bold.type = "none", digits = digits)
  cat(knit_print(lambda.flex))
  cat("Note: loadings flagged when <", load.flag, "in a fold\n  heywood flag is the number of folds the variable's estimated residual variance was negative")
  cat("\n\n")
  if(n > 1){
  cat("**Mean Factor Correlations**")
  cat("\n\n")
  corr.flex <- flextab_format(kcorrs$correlations[[n]], bold.type = "none", digits = digits)
  corr.flex <- flextable::compose(corr.flex, i = 1, j = 1, value = flextable::as_paragraph(""), part = "header")
  cat(knit_print(corr.flex))
  cat("\n\n")
  }
  cat("**Mean Scale Reliabilities**")
  cat("\n\n")
  rel.flex <- flextab_format(as.data.frame(krels$reliabilities[[n]]), bold.type = "none", digits = digits)
  cat(knit_print(rel.flex))
  cat("\n\n")
}

```

\newpage

# Appendix

## Within Fold Model Fit

```{r appendix.fits, ft.align = "left", results='asis'}
index <- if(sum(grepl("df", index)) == 0) c("df", index) else index

ax <- length(index)*length(model.names)
if(ax <= 16){ # is the appendix a reasonable width?
  
  appendix.map <- data.frame(col_keys = names(appendix),
                      top = c("fold", rep(model.names, each = length(index))),
                      bottom = c("fold", rep(index, times = length(model.names))))

appendix.flex <- appendix_wrapper(appendix, appendix.map, border, digits)
appendix.flex
  
  
} else { # If not, split into two tables 

  modsplit <- floor(16/length(index))
colsplit <- 1+length(index)*modsplit
appendix1 <- appendix[1:colsplit]
appendix2 <- appendix[c(1, (colsplit+1):length(appendix))]

appendix1.map <- data.frame(col_keys = names(appendix1),
                           top = c("fold", rep(model.names[1:modsplit], each = length(index))),
                           bottom = c("fold", rep(index, times = modsplit)))

appendix1.flex <- appendix_wrapper(appendix1, appendix1.map, border, digits)
appendix1.flex
# part 2 needs to be in a separate chunk for some reason
}
```

```{r appendix2, ft.align = "left", results='asis'}
if(ax > 16){ 
  appendix2.map <- data.frame(col_keys = names(appendix2),
                            top = c("fold", rep(model.names[(modsplit+1):length(model.names)], each = length(index))),
                            bottom = c("fold", rep(index, times = length(model.names) - modsplit)))
  appendix2.flex <- appendix_wrapper(appendix2, appendix2.map, border, digits)
  appendix2.flex
}
```


## All EFA Structures

```{r appendix.structures, results = 'asis'}
strux <- kfa$efa.structures
for(n in 1:length(strux)){
  cat("### Factors:", n)
  cat("\n\n")
  for(s in seq_along(strux[[n]])){
    cat("**Factor Structure Option", s, "**")
    cat("\n\n")
    cat("**In Folds:", paste(strux[[n]][[s]]$folds, collapse = ", "), "**")
    cat("\n\n")
    if (strux[[n]][[s]]$structure == "") cat("Structure contained single item factor") else cat(gsub("\n", "\n\n", strux[[n]][[s]]$structure))
    cat("\n\n")
  }
}

```

